---
title: "AlumTracking"
author: "Linli Zhou"
date: "2022-08-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load package}
library(readxl)
library(dplyr)
```

# Research question: 
1. Postgrad Life Basic: 1) How many alumni are employed/unemployed/continue-ed across years? 2) What are the most popular title/degree and employers/institutions?

- variables needed: 1) EMPLOYED, TITLE, EMPLOYER; 2) not/continue-ed+institution/degree
- data source: 1) historical.data append with survey and linkedin; 2)clearinghouse

2. Employ-ability/Continue-edu characteristics: 1) Which major/degree are most employable across years? 2) How demographic (gender, race) correlate with employment?

- variables needed: school/major/degree, gender/race
- data source: ipeds.complete.16-current

3. What are alum's top interests in Lasell alum activities?

- variables needed: INTEREST
- data source: historical.data append with survey

# Data Prep 

## Grad Alumni 6 month

```{r target data}
#gd6m target data
#find sheet
excel_sheets("/Users/linlizhou/Documents/LASELL/data/alumni/2021Grad6m_historic.xlsx")#only one sheet
#read data
gd6m<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/2021Grad6m_historic.xlsx")

#transform data (THE INTEREST COL)
gd6m<-gd6m%>%mutate(interest=case_when(
  Interest_AlumnCareerNetwork=="Alumni Career Network"~"Career Network",
  
  Interest_JobPosts=="Posting jobs or internships listings for Lasell students"~"Post Jobs",
  
  Interest_CareerFair=="Career Fair" | 
    Interest_CollegeFair=="College Fair"~"Career/College Fair",
  
  Interest_Volunteering=="Volunteering at Lasell events" | 
    Interest_CampusPresentation=="Campus presentation to students" | 
    Interest_Mentor=="Being a mentor to current students" ~"Volunteer",
  
Interest_SocialActivities == "Social activities (sporting events, reunion, etc.)" | 
Interest_Recreational=="Recreational programs (kayaking, hiking, etc.)" ~ "Social",
  
   Interest_AcademicCultural=="Academic/Cultural (lectures, theater, etc.)" ~ "Academic/Cultural"
   ))

#select vars for research questions
gd6m_s<-gd6m%>%select(
  PC_ID, 
  `Employed/Ed`, #EMPLOYED VAR
  Employment_Organization, #EMPLOYER VAR
  Employment_JobTitle, #TITLE VAR
  `Average Salary` ##INCOME VAR
)
```

