---
title: ""
header-includes:
    \usepackage{fancyhdr}
    \addtolength{\headheight}{0.7cm}
    \pagestyle{fancyplain} 
    \rhead{\vspace{4mm}\textbf{2022 First Impression Survey Results}}
    \lhead{\includegraphics[height=1.3cm]{/Users/linlizhou/Documents/Rprojects/IR.png}}
    \renewcommand{\headrulewidth}{0pt}
author: ''
date: ""
output: 
  pdf_document:
    latex_engine: xelatex
    fig_height: 2
  word_document:
    toc: no
    reference_docx: /Users/linlizhou/Documents/Rprojects/lasell.report.IN-USE.docx
mainfont: Helvetica Light
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning=FALSE, message=FALSE) #show only results
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R") #run code from saved theme and library

#output:
#  pdf_document: default
#  word_document:
#    reference_docx: /Users/linlizhou/Documents/Rprojects/IR-Projects/lasell_report_template.docx

#output:
#  word_document:
#    toc: yes
#    reference_docx: "/Users/linlizhou/Documents/Rprojects/IR-Projects/lasell_report_template.docx"
    
#output:
#  bookdown::word_document2:
#    fig_caption: yes
#    reference_docx: "/Users/linlizhou/Documents/Rprojects/IR-Projects/lasell_report_template.docx"
```

```{r load and clean data}
#read data
fis<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/First Impressions/2022 Fall/20221013124928-SurveyExport.csv")
```


```{r match ppid from allstu22 for fis}
#fis email rename
fis<-fis%>%
  rename(email=`Please provide your Lasell email address. This information is needed for research purposes. Your personal information will be kept confidential and will not appear on any report. `)

#fis email.short
fis<-fis%>%
  mutate(email.short=gsub("@lasell.edu","",fis$email),#remove extra to keep all values the same format
         email.short=str_to_lower(email.short))%>%  #lower case
  select(-email)#to avoid too many cols get merged



#backup data email
allstu<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Registrar Reports/2022 Fall/Fall 2022 UG Backup Data Report.xlsx")

#select 2022 cohort and vars
allstu22<-allstu%>%
  filter(`Cohort Id`=="2022")%>%#this year's students
  select(`People Code Id`, Name,`Lasell email`,
         `Transfer YN`,`Res/Comm`,Gender,Ethnicity,`FT/PT`)%>%#select all usable vars
  rename(gender=Gender)#to avoid join by "Gender"

#create email.short
allstu22<-allstu22%>%
  mutate(email.short=gsub("@lasell.edu","",allstu22$`Lasell email`),#remove extra to match fis emails
         email.short=str_to_lower(email.short))%>%#keep lower case format
  select(-`Lasell email`)#avoid too many cols get merged


#merge
fis<-left_join(fis,allstu22,by="email.short")#all fis with a valid email will have a ppid and names now
#check: sum(is.na(fis$`People Code Id`));sum(is.na(fis$Name))#only 16 do not find a matched ppid/name
```


```{r select vars and SAVE fis.s}
#select: remove starter cols
fis.s<-fis%>%select(-(`Response ID`:`Date Submitted`),-(`Contact ID`:Source),-(`Invite Custom Field 2`:Gender))%>%#removed 54 cols
  janitor::remove_empty(c("rows", "cols"))#remove empty rows/cols (including header has to be NA), removed 1 rows

#remove NA cols: nothing get removed
fis.s<-fis.s[ , colSums(is.na(fis.s)) < nrow(fis.s)] #sum each col's # of NA rows, as long as not all rows are NA then select them 

#check: names(fis)[names(fis)%in%names(fis.s)==FALSE]
```


```{r one ppid col}
#rename headers
#ppid
#check: sum(is.na(fis.s$`Invite Custom Field 1`));sum(is.na(fis.s$`People Code Id`))#148vs15
fis.s<-fis.s%>%mutate(ppid=if_else(!is.na(`Invite Custom Field 1`),#if settled by field then field
                            `Invite Custom Field 1`,`People Code Id`))%>%#if not settled, then matched id
  select(-`Invite Custom Field 1`,-`People Code Id`)
#check: sum(is.na(fis.s$ppid))#14 without ppid
```


```{r rename cols and SAVE xlsx}
#look at the survey instruction and lapply(fis.s, unique) to do this
fis.s<-fis.s%>%rename(
  RCstatus=`Which of the following describes your status for the 2022 fall semester?`,
#satisfaction 0-6 scale  
  satis.activity=`Campus-wide programs and activities (virtual or in-person)?:Please tell us how satisfied you are with…`,
  satis.activity.cm=`Comment or example::Please tell us how satisfied you are with…...58`,
  
  satis.overallcourse=`Your courses overall so far?:Please tell us how satisfied you are with…`,
  satis.majorcourse=`Your courses within your major so far? (If you are an undeclared major, please leave blank):Please tell us how satisfied you are with…`,
  satis.course.cm=`Comment or example::Please tell us how satisfied you are with…...61`,
  
  satis.acchallenge=`The degree of academic challenge in your courses?:Please tell us how satisfied you are with…`,
  satis.acchallenge.cm=`Comment or example::Please tell us how satisfied you are with…...63`,

  satis.accommit=`Other students' commitment to their studies?:Please tell us how satisfied you are with…`,
  satis.accommit.cm=`Comment or example::Please tell us how satisfied you are with…...65`,
  
  satis.foodav=`Food service availability on campus?:Please tell us how satisfied you are with…`,
  satis.foodav.cm=`Comment or example::Please tell us how satisfied you are with…...67`,
  
  satis.residstaff=`Residential Life staff?:Please tell us how satisfied you are with…`,
  satis.residstaff.cm=`Comment or example::Please tell us how satisfied you are with…...69`,
  
  satis.residhall=`Your living situation in the residence halls?:Please tell us how satisfied you are with…`,
  satis.residhall.cm=`Comment or example::Please tell us how satisfied you are with…...71`,

#connection 0-6 scale  
  connect.faculty=`Faculty?:How connected do you feel to…`,
  connect.faculty.cm=`Comment or example::How connected do you feel to…...73`,
  
  connect.stu=`Other students?:How connected do you feel to…`,
  connect.stu.cm=`Comment or example::How connected do you feel to…...75`,

#emphasis question: 4 text scale  
  emphasize.acsupport=`Using learning support services (tutoring services, writing center, etc):Based on your experience so far, how much does Lasell University emphasize the following?`,
  emphasize.socoppo=`Providing opportunities to be involved socially:Based on your experience so far, how much does Lasell University emphasize the following?`,
  emphasize.campactivity=`Attending campus activities and events (virtual or in-person):Based on your experience so far, how much does Lasell University emphasize the following?`,
  emphasize.issueevents=`Attending events that address important social, economic, or political issues:Based on your experience so far, how much does Lasell University emphasize the following?`,

#satisfaction 0-6 scale
  service.aac=`Academic Achievement Center:Please tell us how satisfied you are with…`,
  service.aac.cm=`Comment or Example::Please tell us how satisfied you are with…...81`,

  service.classtech=`Classroom Technology and Computer Labs:Please tell us how satisfied you are with…`,
  service.classtech.cm=`Comment or Example::Please tell us how satisfied you are with…...83`,

  service.counseling=`Counseling Center (Located at 18 Maple Terrace):Please tell us how satisfied you are with…`,
  service.counseling.cm=`Comment or Example::Please tell us how satisfied you are with…...85`,

  service.acadvisor=`Your academic advisor:Please tell us how satisfied you are with…`,
  service.acadvisor.cm=`Comment or Example::Please tell us how satisfied you are with…...87`,

  service.health=`Health Services (Located in Edwards Student Center):Please tell us how satisfied you are with…`,
  service.health.cm=`Comment or Example::Please tell us how satisfied you are with…...89`,

  service.techhelp=`Technology Help Desk:Please tell us how satisfied you are with…`,
  service.techhelp.cm=`Comment or Example::Please tell us how satisfied you are with…...91`,

  service.shuttle=`Lasell Shuttle:Please tell us how satisfied you are with…`,
  service.shuttle.cm=`Comment or Example::Please tell us how satisfied you are with…...93`,

  service.other=`Please type the service(s) in to the box (i.e. vending, mailroom, washing/drying etc.):Please provide feedback on any other services on campus we have not mentioned in the previous questions.`,
  service.other.cm=`Feedback::Please provide feedback on any other services on campus we have not mentioned in the previous questions.`,

#academic 0-6 scale
  meetacexpect=`Is the college meeting your expectations in terms of academic experience?:Please tell us a little bit about what you think of Lasell's academics.`,
  meetacexpect.cm=`Comment or example::Please tell us a little bit about what you think of Lasell's academics.`,

  faculty.orgmaterial=`Present material in a well-organized way?:How often do your faculty…`,
  faculty.explain=`Make good use of examples and illustrations to explain difficult points?:How often do your faculty…`,
  faculty.prep=`Come to class well prepared?:How often do your faculty…`,
  faculty.command=`Have a good command of what they are teaching?:How often do your faculty…`,

#outside class 0-6 agreement
  interact.outside=`I have had a positive interaction with at least one Lasell faculty or staff member outside of class.:How much do you agree…`,
  interact.cm=`How have you been able to effectively interact with others in the Lasell community in a safe manner so far this semester?`,
  interact.difficulty=`What are the difficulties you’re facing when interacting with others within the Lasell community this semester?`)

#write.xlsx(fis.s,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/First Impressions/2022 Fall/raw_renamed.xlsx")
```

# Survey respondents

```{r respondents vs overall SAVE full df}
#full merge survey data with all population data for background vars comparisions
#data merge full
fis.s<-fis.s%>%mutate(RespondentOverall="Respondents")
allstu22<-allstu22%>%mutate(RespondentOverall="All First-Year")%>%rename(ppid=`People Code Id`)
fulldf<-full_join(fis.s,allstu22)

#response rate
num.response=fulldf%>%filter(RespondentOverall=="Respondents")%>%nrow()
num.overall=fulldf%>%filter(RespondentOverall=="All First-Year")%>%nrow()
response_rate=formattable::percent(num.response/num.overall,digits=0)
```


```{r one RCstatus col in fulldf}
fulldf<-fulldf%>%mutate(Res_Com=if_else(!is.na(RCstatus),#if settled by RC then RC
          RCstatus,`Res/Comm`))%>%#if not settled, then res/com from allstu
  select(-RCstatus,-`Res/Comm`)%>%
  mutate(RCstatus=if_else(Res_Com=="R","Resident",
                          if_else(Res_Com=="C","Commuter",Res_Com)))%>%
  select(-Res_Com)
  
#check: fulldf.t%>%count(RCstatus)
```

```{r recode race in fulldf}
fulldf<-fulldf%>%mutate(Ethnicity=if_else(is.na(Ethnicity),"Race and Ethnicity Unknown",Ethnicity))%>%
  mutate(Ethnicity=if_else(Ethnicity=="Race and Ethnicity Unknown","Unknown",Ethnicity))%>%
  mutate(Ethnicity=if_else(Ethnicity=="Two or more Races","Multi-races",Ethnicity))%>%
  mutate(Ethnicity=if_else(Ethnicity=="Non Resident Alien","International",Ethnicity))%>%
  mutate(Ethnicity=if_else(Ethnicity=="Native Hawaiian or Other Pacific Islander","Native",Ethnicity))%>%
  mutate(Ethnicity=if_else(Ethnicity=="Black or African American","Black",Ethnicity))
```

```{r recode gender}
fulldf<-fulldf%>%mutate(gender=if_else(is.na(gender),"Unknown",gender))
```






```{r left merge allstu22.2}
#left merge survey data with all population data 
allstu22.s<-allstu22%>%select(-RespondentOverall)
allstu22.s<-allstu22.s%>%mutate(ResAll=
                        if_else(ppid%in%fis.s$ppid,#if id is one of the same survey id 
                        "Respond","Not Respond"))
#check: allstu22.s%>%count(ResAll) #314 person, 195 responded, 177 have ppid, 18 no ppid
```

```{r resp_rate,fig.fullwidth=TRUE}
resp_rate<-allstu22.s%>%group_by(ResAll)%>%summarise(cnt=n())%>%
 mutate(prt=round(cnt/sum(cnt)*100,digits = 0))%>%
  ggplot(aes(x=2, y = prt, fill=ResAll)) +#x=2 to place the pie centered on limit
    xlim(0.5, 2.5)+#only show .5-2.5 of pie (0-.5 will be the hole)
  geom_bar(stat="identity")+coord_polar(theta="y",start=0)+#make bar on a circled coord
  scale_fill_manual(values = c("grey","#69b3e7"))+
  annotate("text",x = 0.5, y = 0.5, fontface="bold",#center is 0.5
           label = str_wrap(paste0(response_rate," Response Rate"),10))+#fontface=2 bolded
    theme_lz()+theme(legend.position = "none")+
  labs(#caption=str_wrap("Survey collected: Sep. 20-30, 2022",20),
       title="",x="",y="",fill="",
       subtitle = str_wrap("Survey Collection: Sep 20-30, 2022",20))#+
  #annotate("text",x = 0.5, y = 2.5, label=)
    #geom_text(aes(x =2,label = ResAll),position = position_stack(vjust = .5) )

#response rate
#ResAll.waffle<-fulldf%>%group_by(RespondentOverall)%>%summarise(cnt=n())%>%
 # mutate(prt=round(cnt/sum(cnt)*100,digits = 0))%>%
#ggplot(aes(values = prt, fill=RespondentOverall)) +
 # geom_waffle(color="white",flip = TRUE)+
  # labs(title=str_wrap(paste0(response_rate," Response Rate"),40),#, " (",num.response, " out of ", num.overall,")"),40),#80 is a full line length
   #    x="",y="",fill="", 40)+
       #subtitle=str_wrap("Data collection: Sep 20-30, 2022"),40)+ #shows bottom right
  #theme_lz()+
   # scale_y_discrete(labels=c("Respondents","All First-year"))+
  #scale_fill_manual(values = c("grey","#69b3e7"))#fill legend labels=c(""),name="")
 # geom_text(aes(x = prt, y=RespondentOverall, label=paste0(RespondentOverall,": ",prt)),color="white",position = position_dodge(0.9),hjust=1)

#response rate
#ResAll.number<-fulldf%>%count(RespondentOverall)%>%
#ggplot(aes(x = n, y=RespondentOverall, fill=RespondentOverall)) +
#  geom_col()+
#  labs(title=str_wrap(paste0(response_rate," Response Rate"),40),#, " (",num.response, " out of ", num.overall,")"),40),#80 is a full line length
#       x="",y="",fill="", 40)+
       #subtitle=str_wrap("Data collection: Sep 20-30, 2022"),40)+ #shows bottom right
#  theme_lz()+theme(legend.position = "none")+
    #scale_y_discrete(labels=c("Respondents","All First-year"))+
#  scale_fill_manual(values = c("#69b3e7","grey"))+#fill legend labels=c(""),name="")
#  geom_text(aes(label=paste0(RespondentOverall,": ",n)),color="white",position = position_dodge(0.9),hjust=1)
```


```{r respondent res.com figure}
#background info: gender & ethnicity, FT/PT & Transfer, RC
#RC
ResAll.rcstatus<-fulldf%>%filter(!is.na(RCstatus))%>%
  group_by(RespondentOverall,RCstatus)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits=0))%>%
  
ggplot(aes(x = prt, fill=RespondentOverall, y=RCstatus)) +
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  labs(title=str_wrap("",40),#80 is a full line length
       x="",y="",fill="")+ 
  theme_lz()+
  theme(axis.text.y = element_text(),
        legend.position = "none")+
    scale_y_discrete(labels=c("Commuters","Residents"))+
  geom_text(aes(label=paste0(prt)),size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+#, " ", RCstatus," among ",RespondentOverall
  scale_fill_manual(values = c("grey","#69b3e7"))#+#fill legend labels=c(""),name="")
 # coord_flip()
```

```{r respondent gender figure}
#background info: gender & ethnicity, FT/PT & Transfer, RC
#RC
ResAll.gd<-fulldf%>%filter(gender!="Unknown")%>%
  group_by(RespondentOverall,gender)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits=0))%>%
  
ggplot(aes(x = prt, fill=RespondentOverall, y=gender)) +
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  labs(title=str_wrap("",40),#80 is a full line length
       x="",y="",fill="")+ 
  theme_lz()+
  theme(axis.text.y = element_text(), legend.position = "none")+
    scale_y_discrete(labels=c("Male","Female"))+
  geom_text(aes(label=paste0(prt)),size=3,vjust=0.5,hjust=1.5,fontface="bold",position = position_dodge(0.9))+#, " ", gender," among ",RespondentOverall
  scale_fill_manual(values = c("grey","#69b3e7"))#+#fill legend labels=c(""),name="")
  #coord_flip()
```


```{r respondent ethnicity figure}
ResAll.eth<-fulldf%>%filter(Ethnicity!="Unknown")%>%
  group_by(RespondentOverall,Ethnicity)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits=0))%>%
  
  ggplot(aes(x = prt, fill=RespondentOverall, y=reorder(Ethnicity,(-prt))))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+theme(axis.text.x = element_text(), legend.position = c(0.8,0.5))+
  geom_text(aes(label=paste0(prt)),size=3,fontface="bold",position = position_dodge(0.9))+
  #scale_y_discrete(guide=guide_axis(n.dodge = 2))+
  scale_fill_manual(values = c("grey","#69b3e7"))+#fill legend labels=c(""),name="")
  coord_flip()

#pvttbl<-fulldf%>%filter(Ethnicity!="Unknown")%>%
 # group_by(RespondentOverall,Ethnicity)%>%summarise(cnt=n())%>%
  #mutate(prt=formattable::percent(cnt/sum(cnt),digits=0))

#set_order <- pvttbl%>% filter(RespondentOverall=="All First-Year Students") %>%
 #             arrange(prt) %>%mutate(eth_reorder = factor(Ethnicity))

#ResAll.eth<-pvttbl%>%
#ggplot(aes(x = prt, fill=RespondentOverall, y=Ethnicity)) +
 # geom_bar(stat="identity",position = position_dodge(),width=0.8)+
  #labs(title=str_wrap("",40),#80 is a full line length
   #    x="",y="",fill="") +
  #theme_lz()+
  #theme(axis.text.x = element_text(), legend.position = c(0.5,0.8))+
#  scale_y_discrete(limits = set_order$eth_reorder)+
 # geom_text(aes(label=paste0(prt)),size=3,position = position_dodge(0.9))+
  #scale_fill_manual(values = c("grey","#69b3e7"))+#fill legend labels=c(""),name="")
  #coord_flip()
```

```{r combine 2 first}
fig_gd.rc<-gridExtra::grid.arrange(ResAll.rcstatus, ResAll.gd, nrow=2)
```


```{r respondent_figures,include=TRUE,fig.height=2.5}
gridExtra::grid.arrange(resp_rate,fig_gd.rc, nrow=1, widths=c(1,1))
#layout(matrix(c(1,2,3),nrow=1,ncol=3,byrow = TRUE))
#ResAll.rcstatus+ ResAll.gd+ ResAll.eth +plot_layout(ncol = 3)
```


```{r eth figure, include=TRUE}
ResAll.eth #has to be separate b/d not part of grid.arrange
```







```{r historical data}
historical<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/First Impressions/2022 Fall/HistoricalItems.xlsx")

historical$`2018`<-as.numeric(historical$`2018`)

historical<-tidyr::pivot_longer(historical,cols=c(`2018`:`2021`),names_to = "year",values_to = "prt")
```

```{r current data - consider NA as also "have not used"}
fis%>%count(Status=="Complete")
```



```{r current data - distill one satis number}
#check: lapply(fis.s[,str_detect(names(fis.s),"cm$")==FALSE],unique)%>%View()
##satis.t
satis.t1<-fis.s%>%filter(!is.na(satis.activity))%>%#remove NA from total
  group_by(satis.activity)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.activity>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.activity")%>%select(item,year,prt)#select needed vars and values

satis.t2<-fis.s%>%filter(!is.na(satis.overallcourse))%>%#remove NA from total
  group_by(satis.overallcourse)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.overallcourse>3,"Satisfied","Dissadisfied"))%>%
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.overallcourse")%>%select(item,year,prt)

satis.t3<-fis.s%>%filter(!is.na(satis.majorcourse))%>%#remove NA from total
  group_by(satis.majorcourse)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.majorcourse>3,"Satisfied","Dissadisfied"))%>%
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.majorcourse")%>%select(item,year,prt)

satis.t4<-fis.s%>%filter(!is.na(satis.acchallenge))%>%#remove NA from total
  group_by(satis.acchallenge)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.acchallenge>3,"Satisfied","Dissadisfied"))%>%
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.acchallenge")%>%select(item,year,prt)

satis.t5<-fis.s%>%filter(!is.na(satis.accommit))%>%#remove NA from total
  group_by(satis.accommit)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.accommit>3,"Satisfied","Dissadisfied"))%>%
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.accommit")%>%select(item,year,prt)

satis.t6<-fis.s%>%filter(!is.na(satis.foodav))%>%#remove NA from total
  group_by(satis.foodav)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.foodav>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.foodav")%>%select(item,year,prt)

satis.t7<-fis.s%>%filter(!is.na(satis.residstaff))%>%#remove NA from total
  group_by(satis.residstaff)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.residstaff>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.residstaff")%>%select(item,year,prt)

satis.t8<-fis.s%>%filter(!is.na(satis.residhall))%>%#remove NA from total
  group_by(satis.residhall)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(satis.residhall>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="satis.residhall")%>%select(item,year,prt)


##emphasize faculty and connect
#emphasize
emp1<-fis.s%>%filter(!is.na(emphasize.acsupport))%>%#remove NA from total
  group_by(emphasize.acsupport)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(emphasize.acsupport%in%c("Very much","Quite a bit"),
                         "Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="emphasize.acsupport")%>%select(item,year,prt)

emp2<-fis.s%>%filter(!is.na(emphasize.socoppo))%>%#remove NA from total
  group_by(emphasize.socoppo)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(emphasize.socoppo%in%c("Very much","Quite a bit"),
                         "Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="emphasize.socoppo")%>%select(item,year,prt)

emp3<-fis.s%>%filter(!is.na(emphasize.campactivity))%>%#remove NA from total
  group_by(emphasize.campactivity)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(emphasize.campactivity%in%c("Very much","Quite a bit"),
                         "Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="emphasize.campactivity")%>%select(item,year,prt)

emp4<-fis.s%>%filter(!is.na(emphasize.issueevents))%>%#remove NA from total
  group_by(emphasize.issueevents)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(emphasize.issueevents%in%c("Very much","Quite a bit"),
                         "Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="emphasize.issueevents")%>%select(item,year,prt)

expect.t1<-fis.s%>%filter(!is.na(meetacexpect))%>%#remove NA from total
  group_by(meetacexpect)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(meetacexpect>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="meetacexpect")%>%select(item,year,prt)
#faculty
faculty.t1<-fis.s%>%filter(!is.na(faculty.orgmaterial))%>%#remove NA from total
  group_by(faculty.orgmaterial)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(faculty.orgmaterial>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="faculty.orgmaterial")%>%select(item,year,prt)

faculty.t2<-fis.s%>%filter(!is.na(faculty.explain))%>%#remove NA from total
  group_by(faculty.explain)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(faculty.explain>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="faculty.explain")%>%select(item,year,prt)

faculty.t3<-fis.s%>%filter(!is.na(faculty.prep))%>%#remove NA from total
  group_by(faculty.prep)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(faculty.prep>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="faculty.prep")%>%select(item,year,prt)

faculty.t4<-fis.s%>%filter(!is.na(faculty.command))%>%#remove NA from total
  group_by(faculty.command)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(faculty.command>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="faculty.command")%>%select(item,year,prt)

#connect.t1<-mean(fis.s$connect.faculty, na.rm = TRUE)
#connect.t2<-mean(fis.s$connect.stu, na.rm = TRUE)
connect.t1<-fis.s%>%filter(!is.na(connect.faculty))%>%#remove NA from total
  group_by(connect.faculty)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(connect.faculty>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="connect.faculty")%>%select(item,year,prt)

connect.t2<-fis.s%>%filter(!is.na(connect.stu))%>%#remove NA from total
  group_by(connect.stu)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(connect.stu>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="connect.stu")%>%select(item,year,prt)

connect.t3<-fis.s%>%filter(!is.na(interact.outside))%>%#remove NA from total
  group_by(interact.outside)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(interact.outside>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="interact.outside")%>%select(item,year,prt)

## service.satis
service.s1<-fis.s%>%filter(!is.na(service.aac)&service.aac!="Have not use")%>%#remove NA from total
  group_by(service.aac)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.aac>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="service.aac.satis")%>%select(item,year,prt)

service.s2<-fis.s%>%filter(!is.na(service.classtech)&service.classtech!="Have not use")%>%#remove NA from total
  group_by(service.classtech)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.classtech>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="service.classtech.satis")%>%select(item,year,prt)

service.s3<-fis.s%>%filter(!is.na(service.counseling)&service.counseling!="Have not use")%>%#remove NA from total
  group_by(service.counseling)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.counseling>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="service.counseling.satis")%>%select(item,year,prt)

service.s4<-fis.s%>%filter(!is.na(service.acadvisor)&service.acadvisor!="Have not met with advisor")%>%#remove NA from total
  group_by(service.acadvisor)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.acadvisor>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="service.acadvisor.satis")%>%select(item,year,prt)

service.s5<-fis.s%>%filter(!is.na(service.health)&service.health!="Have not use")%>%#remove NA from total
  group_by(service.health)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.health>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="service.health.satis")%>%select(item,year,prt)

service.s6<-fis.s%>%filter(!is.na(service.techhelp)&service.techhelp!="Have not use")%>%#remove NA from total
  group_by(service.techhelp)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.techhelp>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="service.techhelp.satis")%>%select(item,year,prt)

service.s7<-fis.s%>%filter(!is.na(service.shuttle)&service.shuttle!="Have not use")%>%#remove NA from total
  group_by(service.shuttle)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.shuttle>3,"Satisfied","Dissadisfied"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Satisfied")%>%mutate(year="2022",item="service.shuttle.satis")%>%select(item,year,prt)
```

```{r service.use - NA values also considered as "have not used"}
## service.use
service.u1<-fis.s%>%filter(Status=="Complete")%>%#only completed survey responses for accurate donominator
  group_by(service.aac)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.aac=="Have not use"|is.na(service.aac),"Not-use","Used"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Used")%>%mutate(year="2022",item="service.aac.use")%>%select(item,year,prt)

service.u2<-fis.s%>%filter(Status=="Complete")%>%#only completed survey responses for accurate donominator
  group_by(service.classtech)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.classtech=="Have not use"|is.na(service.classtech),"Not-use","Used"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Used")%>%mutate(year="2022",item="service.classtech.use")%>%select(item,year,prt)

# fis.s%>%count(service.counseling)
service.u3<-fis.s%>%filter(Status=="Complete")%>%#only completed survey responses for accurate donominator
  group_by(service.counseling)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.counseling=="Have not use"|is.na(service.counseling),"Not-use","Used"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Used")%>%mutate(year="2022",item="service.counseling.use")%>%select(item,year,prt)

service.u4<-fis.s%>%filter(Status=="Complete")%>%#only completed survey responses for accurate donominator
  group_by(service.acadvisor)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.acadvisor=="Have not met with advisor"|is.na(service.acadvisor),"Not-use","Used"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Used")%>%mutate(year="2022",item="service.acadvisor.use")%>%select(item,year,prt)

service.u5<-fis.s%>%filter(Status=="Complete")%>%#only completed survey responses for accurate donominator
  group_by(service.health)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.health=="Have not use"|is.na(service.health),"Not-use","Used"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Used")%>%mutate(year="2022",item="service.health.use")%>%select(item,year,prt)

service.u6<-fis.s%>%filter(Status=="Complete")%>%#only completed survey responses for accurate donominator
  group_by(service.techhelp)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.techhelp=="Have not use"|is.na(service.techhelp),"Not-use","Used"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Used")%>%mutate(year="2022",item="service.techhelp.use")%>%select(item,year,prt)

service.u7<-fis.s%>%filter(Status=="Complete")%>%#only completed survey responses for accurate donominator
  group_by(service.shuttle)%>%summarise(cnt=n())%>%#count each 6 groups
  mutate(regroup=if_else(service.shuttle=="Have not use"|is.na(service.shuttle),"Not-use","Used"))%>%#converge to 2 group
  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
  filter(regroup=="Used")%>%mutate(year="2022",item="service.shuttle.use")%>%select(item,year,prt)
```


```{r service.use - wrong approach: only "have not used" is "have not used"}
## service
#service.u1<-fis.s%>%filter(!is.na(service.aac))%>%#remove NA from total
#  group_by(service.aac)%>%summarise(cnt=n())%>%#count each 6 groups
#  mutate(regroup=if_else(service.aac=="Have not use","Not-use","Used"))%>%#converge to 2 group
#  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
#  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
#  filter(regroup=="Used")%>%mutate(year="2022",item="service.aac.use")%>%select(item,year,prt)

#service.u4<-fis.s%>%filter(!is.na(service.acadvisor))%>%#remove NA from total
#  group_by(service.acadvisor)%>%summarise(cnt=n())%>%#count each 6 groups
#  mutate(regroup=if_else(service.acadvisor=="Have not met with advisor","Not-use","Used"))%>%#converge to 2 group
#  group_by(regroup)%>%summarise(regroup.cnt=sum(cnt))%>%#group regrouped and sum previous cnt
#  mutate(prt=formattable::percent(regroup.cnt/sum(regroup.cnt),digits = 0))%>%#prt within regroups
#  filter(regroup=="Used")%>%mutate(year="2022",item="service.acadvisor.use")%>%select(item,year,prt)
```


```{r merged current data}
current<-rbind(connect.t1,connect.t2,connect.t3,
      emp1,emp2,emp3,emp4,
      expect.t1,
      faculty.t1,faculty.t2,faculty.t3,faculty.t4,
      satis.t1,satis.t2,satis.t3,satis.t4,satis.t5,satis.t6,satis.t7,satis.t8,
      service.s1,service.s2,service.s3,service.s4,service.s5,service.s6,service.s7,
      service.u1,service.u2,service.u3,service.u4,service.u5,service.u6,service.u7)
```

```{r merge hist and current and SAVE prtdf}
historical.prt<-historical%>%filter(prt<1)%>%mutate(prt=formattable::percent(prt,digits = 0))
prtdf<-full_join(current,historical.prt)%>%unique()

#save: 
#write_xlsx(prtdf, "/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/First Impressions/2022 Fall/satisfaction18-22.xlsx")

#check: 
#prtdf%>%count(item)%>%View()
#sample_needed=Z^2*p*(1-p)/MOE^2
#margin of error=Z*p/sqrt(sample_n)
```


# Satisfaction
```{r satis1-8}
#satis.4: satis.acchallenge, satis.accommit, satis.majorcourse, satis.overallcourse
satis.aca.figure<-prtdf%>%filter(item%in%c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit"),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+
  theme(legend.position = "top",
        plot.margin=unit(c(2,1,1,-1),"cm"))+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit"),labels = c(str_wrap("Overall Courses",10),
                             str_wrap("Major Courses",10),
                             str_wrap("Academic Challenge",10),
                             str_wrap("Academic Commitment",10))),nrow=1,
             strip.position="bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit")), 
                linetype=factor(item,levels =c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit"))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#6C6F70","#6C6F70","#6C6F70","#6C6F70"))+
  scale_linetype_manual(name="",values=c("dashed","dashed","dashed","dashed"))

#satis.4: satis.activity, satis.foodav, satis.residhall, satis.residstaff
satis.life.figure<-prtdf%>%filter(item%in%c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall"),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+theme(legend.position = "none")+
  geom_text(aes(label= ifelse(year==2022&prt>.8,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year==2022&prt<.8,as.character(round(prt,2)),"")),
            size=3,color="#641F45",vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall"),labels = c(str_wrap("Campus Activity",10),
                             str_wrap("Food Availability",10),
                             str_wrap("Residential Staff",10),
                             str_wrap("Residence Hall",10))),nrow=1, strip.position="bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall")), 
                linetype=factor(item,levels =c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall"))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#6C6F70","#6C6F70","#6C6F70","#6C6F70"))+#lightyellow#FFCB4F
  scale_linetype_manual(name="",values=c("dashed","dashed","dashed","dashed"))
```

## Academic Satisfaction

```{r satis figure, include=TRUE,fig.height=2.5}
satis.aca.figure
```

## Life Satisfaction

```{r satis.life figure, include=TRUE, fig.height=1.5}
satis.life.figure
```


# Services
```{r service1-7.use/.satis}
#service.use: "service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" 
service.use.figure<-prtdf%>%filter(item%in%c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" ),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+theme(legend.position = "top",plot.margin=unit(c(2,1,1,-1),"cm"))+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.2,hjust=.4,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.2,hjust=.4,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" ),
                     labels = c(str_wrap("Academic Achievement Center",10),
                                str_wrap("Academic Advisor",10),
                                str_wrap("Class Technology",10),
                                str_wrap("Tech HelpDesk",10),
                                str_wrap("Counseling Center",10),
                                str_wrap("Health Center",10),
                                str_wrap("Shuttle",10))),nrow=1,strip.position = "bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" )), 
                linetype=factor(item,levels =c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" ))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#FFCB4F","#FFCB4F","#6C6F70","#6C6F70","#6C6F70","#641F45","#6C6F70"))+
  scale_linetype_manual(name="",values=c("solid","solid","dashed","dashed","dashed","solid","dashed"))

#service.satis:"service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" 
service.satis.figure<-prtdf%>%filter(item%in%c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" ),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+theme(legend.position = "none",legend.direction = "vertical")+
  #theme(plot.title = element_text(hjust = 0, vjust = -1))+#,plot.margin = margin(1,0,0,0,"cm"))+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.5,hjust=.4,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.5,hjust=.4,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" ),
                     labels = c(str_wrap("Academic Achievement Center",10),
                                str_wrap("Academic Advisor",10),
                                str_wrap("Class Technology",10),
                                str_wrap("Tech HelpDesk",10),
                                str_wrap("Counseling Center",10),
                                str_wrap("Health Center",10),
                                str_wrap("Shuttle",10))),nrow=1,strip.position = "bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" )), 
                linetype=factor(item,levels =c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" ))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#6C6F70","#6C6F70","#6C6F70","#FFCB4F","#FFCB4F","#6C6F70","#6C6F70"))+
  scale_linetype_manual(name="",values=c("dashed","dashed","dashed","solid","solid","dashed","dashed"))
```

## Services Usage

```{r service figure, include=TRUE,fig.height=3}
service.use.figure
```


## Services Satisfaction
```{r service.satis figure, include=TRUE, fig.height=1.5}
service.satis.figure
```

# Academic and Social Support
```{r making faculty.connect fig}
#empashize4: "emphasize.acsupport", "emphasize.socoppo", "emphasize.campactivity", "emphasize.issueevents"
emp.figure<-prtdf%>%filter(item%in%c("emphasize.acsupport", "emphasize.socoppo", "emphasize.campactivity", "emphasize.issueevents","connect.faculty", "connect.stu"),year=="2022")%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(x = prt, y=reorder(item,prt)))+
  geom_bar(fill="#69b3e7", stat="identity",position = position_dodge(),width=0.8)+
  labs(title=str_wrap("",40),x="",y="") +
  theme_lz()+theme(legend.position = "none",axis.text.y = element_text())+
  geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,
            size=3,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
            size=3,color="#641F45",fontface="bold",position = position_dodge(0.9))+
  scale_y_discrete(labels=c("Issue-based Events","Connected to Faculty","Connected to Students","Social Opportunity","Campus Activity","Academic Support"))
  

#faculty4: "faculty.command", "faculty.explain", "faculty.orgmaterial", "faculty.prep"
faculty.figure<-prtdf%>%filter(item%in%c("faculty.command", "faculty.explain", "faculty.orgmaterial", "faculty.prep","meetacexpect","interact.outside"),year=="2022")%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(x = prt, y=reorder(item,prt)))+
  geom_bar(fill="#69b3e7", stat="identity",position = position_dodge(),width=0.8)+
  labs(title=str_wrap("",40),x="",y="") +
  theme_lz()+theme(legend.position = "none",axis.text.y = element_text())+
  geom_text(aes(label= as.character(round(prt,2))),hjust=1.2,
            size=3,fontface="bold",position = position_dodge(0.9))+
  scale_y_discrete(labels=c("Interact with Staff/Faculty Outside of Class","Meet Academic Expectation","Faculty Explain Materials Well","Faculty Command of Teaching","Faculty Well-Organized","Faculty Well-Prepared"))
 
```

## 2022 Academic and Social Support

```{r empfaculty,include=TRUE}
gridExtra::grid.arrange(faculty.figure,emp.figure, nrow=1, widths=c(1,1))
```




```{r numeric vars/groups and SAVE fis.num}
#remove qual vars
fis.num<-fis.s[, !grepl("cm$",names(fis.s))]%>%
            select(Ethnicity,satis.activity:interact.outside)%>%
            select(-service.other)
#recode services
fis.num<-fis.num %>%mutate(across(starts_with("service."),
                  \(x) `is.na<-`(x, grepl("Have not use|Have not met with advisor", x))),
#recode emphasize
                  across(starts_with("emphasize"),
                  ~ case_when(. =="Very Little" ~ 1, 
                              . =="Some" ~ 2, 
                              . =="Quite a bit" ~ 3, 
                              . =="Very much" ~ 4)))
#change recoded service and emphasize to num
fis.num<-fis.num %>% mutate(across(starts_with(c("emphasize.","service.")),as.numeric))
#check:lapply(fis.num, unique);
#str(fis.num)

#group satis, connect, faculty outcome together
fis.num<-fis.num%>%mutate(satis=rowSums(.[grepl("^satis.",names(.)) & !grepl(".cm$",names(.))]),
  #select[] vars based on & conditions; 
  #default: na.rm=false: one NA then NA so that only all answered are compared
  connect=rowSums(.[grepl("^connect.",names(.)) & !grepl(".cm$",names(.))]),
  emphasize=rowSums(.[grepl("^emphasize.",names(.)) & !grepl(".cm$",names(.))]),
  service=rowSums(.[grepl("^service.",names(.)) & !grepl(".cm$",names(.))]),
  faculty=rowSums(.[grepl("^faculty.",names(.)) & !grepl(".cm$",names(.))]))

#group by aca, life, soc
fis.num<-fis.num%>%mutate(
  academic=satis.overallcourse+satis.majorcourse+satis.acchallenge+satis.accommit+emphasize.acsupport+service.aac+service.classtech+service.acadvisor+meetacexpect+faculty,
  
  life=satis.foodav+satis.foodav+satis.residhall+service.counseling+service.health+service.techhelp+service.shuttle,
  
  soc=satis.activity+connect+emphasize.socoppo+emphasize.campactivity+emphasize.issueevents+interact.outside)

#check
lapply(fis.num, unique)
```

```{r fulldf.num}
#find numeric format vars: historical%>%arrange(-prt)%>%View()
historical.num<-historical%>%filter(item%in%c("faculty","emphasize") |
                    grepl("^connect.",historical$item))
#calculate numeric values of corresponding vars in historical df
current.num<-tibble(faculty=round(mean(fis.num$faculty,na.rm=T)/
                                  length(fis.num[grepl("^faculty.",names(fis.num))]),
                                  digits = 2),
                 connect.faculty=round(mean(fis.num$connect.faculty,na.rm=T),digits = 2),
                 connect.stu=round(mean(fis.num$connect.stu,na.rm=T),digits = 2),
                   emphasize=round(mean(fis.num$emphasize,na.rm=T)/
                                  (length(fis.num[grepl("^emphasize.",names(fis.num))])-1),
                  #emphasize previously only count 3 (without "emphasize.socoppo")
                                   digits = 2))%>%
  mutate(year="2022")%>%
  pivot_longer(cols = c(faculty,connect.faculty,connect.stu,emphasize),names_to = "item",values_to = "prt")
#row bind together
numdf<-rbind(historical.num,current.num)%>%filter(!is.na(prt))%>%arrange(item)

#viz
num.figure<-numdf%>%filter(year>2019)%>%
  #group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+theme(legend.position = "right",legend.direction = "vertical")+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("faculty", "connect.faculty", "connect.stu","emphasize"),labels = c(str_wrap("Faculty Teaching",10),
                             str_wrap("Faculty Connection",10),
                             str_wrap("Student Connection",10),
                             str_wrap("Academic/Social Emphasis",10))),nrow=1,
             strip.position="bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("faculty", "connect.faculty", "connect.stu","emphasize")), 
                linetype=factor(item,levels =c("faculty", "connect.faculty", "connect.stu","emphasize"))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#FFCB4F","#6C6F70","#FFCB4F","#641F45"))+
  scale_linetype_manual(name="",values=c("solid","dashed","solid","solid"))
```



## Historical Academic and Social Support (on scale of 1-6)

```{r numfigure, include=TRUE, fig.height=1.7}
num.figure
```




```{r hypothesis test options}
#最严格
#cor.test(numeric, numeric)


##NumY
#t.test(NumY~ 2CatX) #Cat: category; num: numeric = continuous/ordinal
#wilcox.test(NumY~ 2CatX, paired=FALSE/TRUE)#not-normal distribution t.test
#aov(NumY~ 3+CatX) 
#kruskal.test(NumY, CatX) #not-normal distribution anova
#lm(NumY~anyX+..)



#CrossTable(propX, propY)
#CrossTable(CatX, CatY)
#glm(CatY~anyX, family = "binomial")# logistic regression: generalized linear model
```


```{r try ethnicity with each outcome vars}
#check N: fis.num%>%count(Ethnicity)
summary(lm(service~Ethnicity,data=fis.num))
summary(lm(life~Ethnicity,data=fis.num))
#viz the difference
#fis.num%>%group_by(Ethnicity)%>%summarise(svmn=mean(service,na.rm=TRUE))%>%
#  filter(svmn>0,!is.na(Ethnicity))%>%
#  ggplot(aes(x=Ethnicity,y=svmn))+geom_bar(stat="identity")
#viz together as points
#fis.num%>%filter(Ethnicity %in% c("Black or African American","Hispanic","White"))%>%
#  ggplot(aes(x=life,y=service))+geom_point(aes(color=Ethnicity))#+geom_line(aes(color=Ethnicity))

#further investigate which service/life: found conseling
mod<-lm(service.counseling~Ethnicity,data=fis.num)
summary(mod)#options(scipen=999)#options(scipen=0)
jtools::summ(mod, digits = 1)#broom::tidy(mod, conf.int = TRUE)

#viz the difference
#fis.num%>%filter(Ethnicity %in% c("Black or African American","Hispanic","White","Race and Ethnicity Unknown","Two or more Races"))%>%
#  ggplot(aes(x=Ethnicity,y=service.counseling,label=Ethnicity))+
#  geom_point()+geom_text()+
#  geom_jitter(aes(color=Ethnicity))
#  #+geom_line(aes(color=Ethnicity))
  
ethdiff<-fis.num%>%group_by(Ethnicity)%>%summarise(svmn=mean(service.counseling,na.rm=TRUE))%>%
  filter(svmn>0,!is.na(Ethnicity),Ethnicity!="Race and Ethnicity Unknown")%>%
  ggplot(aes(x=reorder(Ethnicity,(-svmn)),y=svmn))+
  geom_point(size=10,color="#69b3e7")+
  geom_text(aes(label=round(svmn,digits = 1)),fontface="bold")+
  theme_lz()+
  theme(axis.text.x =element_text(face = 'bold'),axis.text.y =element_text(face = 'bold'))+
  labs(title=str_wrap("",40),x="",y="",
       caption="*Counseling service is the only survey item significantly different by ethnicity")+
  scale_x_discrete(labels=c("Hispanic","Black","White","Asian","Multi-races"))+
  scale_y_continuous(limits = c(1,6), 
                     breaks=(seq(1, 6, 1)),
                     labels=c("Extremely Dissatisfied","2","3","4","5","Extremely Satisfied"))
  

  #scale_y_continuous(breaks = seq(1, 6, by = 1) ,labels=scales::percent_format(accuracy = 1))
  #scale_y_discrete(labels=c("Extremly Dissatisfied","","","","","Extremly Satisfied"))
```

# Difference by Ethnicity

## Satisfaction for Counseling Service

```{r ethdiff, include=TRUE}
ethdiff
```





```{r lm}
#outcome vars: meetexpect, satis, connect, emphasize, faculty
#cor.test(fis.num$connect,fis.num$faculty)
#cor.test(fis.num$connect,fis.num$satis)
#cor.test(fis.num$connect,fis.num$satis)

#satis as outcome
# data containing lm Xfactors (excluding satis. cols)
#fis.l<-fis.num%>%select(-starts_with(c("satis.","service.")),#have to remove service due to na results in lm model
#                      -connect,-faculty,-emphasize,-service)
#check:lapply(fis.l, unique)
#lm model: found meetacexpect, interact.outside, emphasize.campactivity, faculty.explain
#summary(lm(satis~.,data=fis.l))

#visualize difference

```




```{r merging factors}
#dmt22fa<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Datamart Files/Test Run of Data Mart/FALL 2022/Test_run_datamart_FALL_ALL_sessions_20220926.xlsx")
#see values for better select vars: dmt22fa%>%filter(ADMIT_YEAR=="2022")%>%select(COHORT:TRANSFERED_CREDITS_CUM)%>%lapply(., unique)
#dmt22fa.s<-dmt22fa%>%select(PC_ID,BIRTHDATE,PARENTS_DEGREE,PARENTS_ATTENDED_COLL,ADMIT_TYPE,
#                 ADMIT_STATE,SCHOOL_GEOMARKET_DESC,BPS_EXAM_YN,HS_GPA,HOME_GEOMARKET_DESC,LV_EMP_YN,APPLICATION_SOURCE,
#                 starts_with(c("FA_LOANS","FA_GRNTS","FINAID_EFC","FA_EFC")),
#                 FINAID_GRANTS_INST_RANGE,FA_Pell_ELIGIBLE_YN,FINAID_ACTUAL_AMT,
                 
#                 INTENDED_MAJOR,MAJOR_1,ACADEMIC_DEPT,REGISTRAR_DEPT,LASELL_WORKS_YN,FYS_COMB,FYS_SECTION,ADVISOR_FULL_NAME,
#                 SESS_REG_CREDITS,REG_PRIOR_CUM_CREDIT,
#                 REG_PRIOR_CUM_CREDIT,REG_PRIOR_CUM_CREDIT,SESS_REG_CREDITS,
#                 TERM_CREDITS_ATTEMPTED,TERM_CREDITS_TOT,TERM_CREDITS_GPA,
#                 TERM_COURSE_COUNT)%>%unique()%>%
#          subset(.,select=which(!duplicated(names(.)))) # Drop Duplicated Columns
#merge to fis.num
#fis.num<-left_join(fis.num,dmt22fa.s,by=c("ppid"="PC_ID"))
##check: sapply(lapply(fis.num, unique),length) if 1 or 2 (one is NA, then is the same as 1)
##found: `Transfer YN`,RCstatus,RespondentOverall,`FT/PT`,Status,BPS_EXAM_YN,FINAID_EFC_IM_RANGE
##all that works: select(satis:SCHOOL_GEOMARKET_DESC,HS_GPA:FINAID_EFC_FM_RANGE,FA_EFC_FM:TERM_COURSE_COUNT)
```


```{r satis outcome - gender diff/reg-factor}
#select factors
#fis.l<-fis.num%>%select(satis,connect,faculty,Ethnicity)
#lm model
#mod<-lm(satis~., data=fis.l)#cannot add "RCstatus" becuase n of commuter is too small that lm method think it has no variance
#summary(mod)

##remove no diff: FINAID_ACTUAL_AMT =FINAID_GRANTS_INST_RANGE,PARENTS_ATTENDED_COLL,MAJOR_1,BIRTHDATE,ADMIT_TYPE,TERM_COURSE_COUNT,FA_Pell_ELIGIBLE_YN,FINAID_ACTUAL_AMT,FA_GRNTS_TOT$,FA_LOANS_TOT$
##has uninterretable diff: ADMIT_STATE,PARENTS_DEGREE,Ethnicity,FINAID_EFC_FM_RANGE,HS_GPA
```









# Summary
## Strengths
* Academic satisfaction remain high (over 90% on average) among first-year students
* Usage of academic achievement center and academic adviser have increased for first-year students
* First-year students' satisfaction towards Tech HelpDesk and Counseling Center have increased
* Teaching quality for first-year courses has been increasing steadily over the past three years
* Connection among first year students increased compared to previous years
* First-year students from Hispanic and Black ethnicity are highly satisfied with counseling services

## Opportunities
* Food availability can be improved
  + First-year students want late night and weekend hours for food
* More events and activities to help first-year students feel socially supported
  + "Connections need time and opportunity to build"
* Counseling center may take a closer look at experiences of first-year students from Asian and multi-races ethnicity

```{r SAVE qual}
qual<-fis.s[,str_detect(names(fis.s),".cm$|difficulty")]%>%janitor::remove_empty(c("rows", "cols"))
qual.emp<-qual%>%select(satis.foodav.cm,service.health.cm,connect.faculty.cm,connect.stu.cm)
  
#tried analysis, but cannot save list
#qual.s<-lapply(qual, unique)
#qual.s<-gsub("NA|\n|\"","",qual.s)#remove NA, remove \n, remove \"
#gsub("NA|\n|\"|c(|)","",qual.s)

#save
#openxlsx::write.xlsx(list('AllCm' = qual,'ImpCm' = qual.emp), file = '/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/First Impressions/2022 Fall/qualcm.xlsx') 
```
























