---
title: "FacultyTenureAnalysis"
author: "Linli Zhou"
format: pptx
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning=FALSE, message=FALSE, fig.align = "center")
#theme
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")  #run code from saved r script
#load data
data<-read_excel("/Users/linlizhou/Documents/LASELL/Faculty Data for Analyst Candidates.xlsx")
```

# Research Questions

1. How has the proportion of tenure-line (TL) and non-tenure-line (NTL) faculty **changed over time**?

2. How has the proportion of TL faculty in certain **rank, racial, or sex** groups changed over time?

3. How has the proportion of TL and NTL faculty changed over time for different **departments**?

```{r clean, results='hide'}
#remove duplicated rows
data<-unique(data)#from 4003 to 3984 observations
#investigate duplicated ID/persons
unique(data$ID)%>%length()#1147 unique ID
data%>% group_by(ID) %>% summarise(cnt=n()) %>%arrange(-cnt) %>%filter(cnt>1) #815 duplicated IDs
#thus, need n_distinct ID in the following codes
```

# Historical Trends

::: notes
- Tenured percentage has been increased since 2016 from 40% to 44% in 2021, with 2020 being the highest 45%. 
- Non-Tenure-line Faculty percentage has been decreased from 60% to 56%, with 2020 being the lowest 55%. 
- There are still 12% less Tenure-line Faculty than non tenured.
::: 

```{r unique TvsN across year}
data%>%group_by(Year, `Tenure Status`)%>%
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%

ggplot(aes(color=factor(`Tenure Status`),x=factor(Year),y=prt,group=factor(`Tenure Status`)))+geom_line()+
geom_text(aes(label=prt),fontface="bold", size = 9)+
theme_lz_ppt()+
scale_y_continuous(breaks = seq(.4,.6,by=.05),labels = scales::percent)+
labs(title=str_wrap("Proportion of Faulcty in Different Tenured Status",50),x="",y="")+
scale_color_discrete(labels=c("Non-tenure","Tenure"),name="")+
theme(axis.text.y=element_blank())
```

# Historical Trends Breakdown: Faculty Rank

::: notes
- Assistant professor tenure-line proportion dropped from 63% in 2016 to 57% in 2017 and became the lowest across professor ranks. However, the proportion but has been increasing ever since and reached 75% in 2021. 
- Professor experienced a slight drop from 68% in 2016 to 65% in 2018, but has increased ever since and reached 73% in 2021. 
- Associate professor has slight increase from 63% in 2016 to 66% in 2019, but dropped to 60% in 2021. 
::: 

```{r tenured trend by rank}
#pivot table
data%>% filter(Rank=="Professor"|Rank=="Assistant Professor"| Rank=="Associate Professor")%>%
  group_by(Year, Rank,`Tenure Status`)%>%#2016 professor as a group -> proportions of (non) tenure for all professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")%>%
  
#plot
ggplot(aes(color=factor(Rank),linetype=factor(Rank),x=factor(Year),y=prt,group=factor(Rank)))+geom_line()+
geom_text_repel(aes(label=prt),fontface="bold",size=6.5)+
  
#themes
scale_y_continuous(breaks = seq(.55,.75,by=.1),labels = scales::percent)+
scale_color_discrete(name="")+
scale_linetype_discrete(name="")+
 
theme_lz_ppt()+theme(axis.text.y=element_blank())+
labs(title="Tenure-line Faculty of Different Ranks",x="",y="")
```


# Historical Trends Breakdown: Race

::: notes
- White faculties have the most stable tenured proportion -- within the 42-48% range. 
- Asian faculties experienced two dropped in 2018 and 2020 and only has 31-32% tenured proportion. The tenured proportion increased from 31% to 51% in 2021.
- Smaller racial groups have below 30% tenured proportions before 2018. However, their tenured proportion has been increasing since 2018 and reached 46-48% in 2021. 

Omitted details:
- 2017 and 2018 are years that most groups experienced drops except Hispanic faculties. International faculties dropped 7% in 2017 and Black faculties dropped 13% in 2018.  
- Hispanic faculties' tenured proportion has been increasing from 25% in 2016 to 59% in 2020. However, it dropped to 46% and become close to other groups. 




- International faculties have the lowest tenured proportion of 20% in 2016, but the proportion jumped to 50% in 2018 and 2021.
- Hispanic faculties have increased tenured proportion from 33% in 2016 to 59% in 2020, and 55% in 2021, both are the highest among all racial groups in those two years. 
- Black faculties' tenured proportion dropped from 50% in 2017 to 20% in 2018, but has been increasing by 7% each year to 44% in 2020 and kept stable at 45% in 2021.
::: 

```{r facet two race bulk group,fig.width=15}
#race count
nrace<-data%>% filter( !(`Race/Ethnicity`%in% c("Unreported", "Two or More Races",NA)))%>%filter(`Tenure Status`=="Tenure Line")%>%
  group_by(`Race/Ethnicity`)%>%count()%>%arrange(-n)%>%mutate(race=factor(`Race/Ethnicity`))

#create two bulk group and pivot table
racepvt<-data%>%filter( !(`Race/Ethnicity`%in% c("Unreported", "Two or More Races",NA)))%>%mutate(RaceGroup=case_when(
  `Race/Ethnicity` %in% nrace$`Race/Ethnicity`[1:2] ~ "Larger Racial Group",
  `Race/Ethnicity` %in% nrace$`Race/Ethnicity`[3:5] ~ "Smaller Racial Group",))%>%
#pivot table  
  group_by(Year, `Race/Ethnicity`,RaceGroup,`Tenure Status`)%>%#2016 male as a group -> proportions of (non) tenure for all male professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")

#max/min data label
#max.min<-racepvt%>%select(`Race/Ethnicity`,prt)%>%group_by(`Race/Ethnicity`)%>%summarise(max=max(prt),min=min(prt))%>%arrange(min)
  
#plot
racepvt%>%ggplot(aes(x=factor(Year),y=prt,color=factor(`Race/Ethnicity`),linetype=factor(`Race/Ethnicity`),group=factor(`Race/Ethnicity`)))+geom_line()+
  scale_color_manual(name="",limits=nrace$race, values = c("black","blue","chartreuse3","darkgoldenrod","brown1"),labels=c("White","Asian","International","Hispanic","Black"))+  
  scale_linetype_manual(name="",limits=nrace$race, values = c("solid","longdash","twodash","solid","longdash"),labels=c("White","Asian","International","Hispanic","Black"))+
  facet_wrap(~RaceGroup,labeller=labeller(RaceGroup= c(`Larger Racial Group`="Larger Racial Groups (Tenure-line Faculty>100)", `Smaller Racial Group`="Smaller Racial Groups (10<Tenure-line Faculty<100)") ) )+
  
geom_text_repel(aes(label=prt),size=5)+
#themes
scale_y_continuous(breaks = seq(.2,1,by=.2),labels = scales::percent)+
theme_lz_ppt()+theme(axis.text.y=element_text(size=12))+theme(panel.grid.major.y = element_line(color = "grey95"), panel.grid.minor.y = element_line(color = "grey95"))+#theme(legend.position = "right", legend.direction = "vertical")+
  guides(color = guide_legend(nrow = 1, byrow = TRUE))+
labs(title=str_wrap("Tenure-line Faculty in Different Racial Groups",80),x="",y="")
```


# Historical Trends Breakdown: Legal Sex in Different Race

::: notes
Hispanic and White faculties have a consistent gender gap with male faculties have higher tenured proportion than female faculties.
::: 

```{r tenured trend by sex in different race, fig.width=15}
#pivot table
data%>% filter(`Race/Ethnicity`!="Unreported")%>% group_by(Year,`Race/Ethnicity`, `Tenure Status`,`Legal Sex`)%>%#2016 male as a group -> proportions of (non) tenure for all male professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")%>%
#plot
ggplot(aes(color=factor(`Legal Sex`),x=factor(Year),y=prt,group=factor(`Legal Sex`)))+geom_line()+facet_wrap(~`Race/Ethnicity`)+
#geom_text_repel(aes(label=prt),fontface="bold",size=6.5)+
#themes
scale_y_continuous(breaks = seq(.2,.8,by=.2),labels = scales::percent)+
#scale_x_discrete(labels=c())
scale_color_discrete(name="")+
theme_lz_ppt()+theme(axis.text.y=element_text(size=12))+theme(panel.grid.major.y = element_line(color = "grey95"))+
labs(title="Gender Gaps for Tenure-line Faculty",x="",y="")
```


# Departmental Tenure Status



```{r dep groups, results='hide'}
#Department that has top 6 number (unique ID/person) faculty
topdep<-data%>%group_by(Department)%>%summarise(cnt=n_distinct(ID))%>%arrange(-cnt)%>%head()

#check top department's T/NT
data%>%filter(Department %in% topdep[[1]]) %>%
  group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%arrange(-prt)

#make department count as ndep
ndep<-data%>%group_by(Department)%>%summarise(cnt=n_distinct(ID))%>%arrange(-cnt)#

#four groups based on department count
ndep[ndep$cnt>30,]%>%str() #11 giant departments
ndep[ndep$cnt%in%seq(21,30,by=1),]%>%str() #13 large departments
ndep[ndep$cnt%in%seq(5,20,by=1),]%>%str()#14 medium departments
ndep[ndep$cnt<5,]%>%str()#14 small departments
ndep[ndep$cnt>20,]%>%str() #24 large departments
ndep[ndep$cnt>30,]%>%str() #11 giant departments
ndep[ndep$cnt%in%seq(21,30,by=1),]%>%str() #13 large departments
ndep[ndep$cnt%in%seq(5,20,by=1),]%>%str()#14 medium departments
ndep[ndep$cnt<5,]%>%str()#14 small departments

#order based on tenure prt -- exclude those without any tenure
dep.order.t<-data%>%group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  filter(`Tenure Status`=="Tenure Line")%>%arrange(prt)%>%
  mutate(dep.f=factor(Department))

#excluded in order
order.exclude<-data[( data$Department %in% dep.order.t$dep.f ) == FALSE,] %>%group_by(Department)%>%
  summarise(cnt=n_distinct(ID)) %>% arrange(cnt) %>% mutate(dep.xf=factor(Department))
dep.order<-c(order.exclude$dep.xf,dep.order.t$dep.f)
```

```{r dep n>20, fig.height=8}
#first group n>20, 24 large departments
data%>%filter(Department %in% ndep[ndep$cnt>20,1]$Department ) %>%
  group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  ggplot(aes(x=Department,y=prt,fill=`Tenure Status`))+geom_bar(stat = "identity")+
  scale_x_discrete(limits = dep.order[(dep.order %in% ndep[ndep$cnt>20,1]$Department)==TRUE])+
  theme_lz_ppt()+geom_text(aes(label=prt),position = position_stack(),hjust=1,color="white", size = 9)+
  coord_flip()+theme(axis.text.x = element_blank())+
  theme(axis.text.y=element_text(size = 20))+
  scale_fill_discrete(labels=c("Non-tenure","Tenure"),name="")+
  labs(x="",y="", title="Faculty Tenure Status for Large Departments (>20 faculty)")
```

```{r dep n>30}
#first group n>30, 11 giant departments
data%>%filter(Department %in% ndep[ndep$cnt>30,1]$Department ) %>%
  group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  ggplot(aes(x=Department,y=prt,fill=`Tenure Status`))+geom_bar(stat = "identity")+
  scale_x_discrete(limits = dep.order[(dep.order %in% ndep[ndep$cnt>30,1]$Department)==TRUE])+
  theme_lz_ppt()+geom_text(aes(label=prt),position = position_stack(),hjust=1,color="white", size = 9)+
  coord_flip()+theme(axis.text.x = element_blank())+
  theme(axis.text.y=element_text(size = 20))+
  scale_fill_discrete(labels=c("Non-tenure","Tenure"),name="")+
  labs(x="",y="", title="Faculty Tenure Status for Giant Departments (>30 faculty)")
```

```{r dep n21-30}
#13 large departments
data%>%filter(Department %in% ndep[ndep$cnt%in%seq(21,30,by=1),1]$Department ) %>%
  group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  ggplot(aes(x=Department,y=prt,fill=`Tenure Status`))+geom_bar(stat = "identity")+
  scale_x_discrete(limits = dep.order[dep.order %in% 
                                              ndep[ndep$cnt%in%seq(21,30,by=1),1]$Department 
                                            ])+
  theme_lz_ppt()+geom_text(aes(label=prt),position = position_stack(),hjust=1, color="white", size = 9)+
  coord_flip()+theme(axis.text.x = element_blank())+
  theme(axis.text.y=element_text(size = 20))+
  labs(x="",y="",title=str_wrap("Faculty Tenure Status for Large Departments (21-30 faculty)",35))
```

```{r dep n5-20}
#22 medium departments
data%>%filter(Department %in% ndep[ndep$cnt%in%seq(5,20,by=1),1]$Department ) %>%
  group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  ggplot(aes(x=Department,y=prt,fill=`Tenure Status`))+geom_bar(stat = "identity")+
  scale_x_discrete(limits = dep.order[dep.order %in% 
                                              ndep[ndep$cnt%in%seq(5,20,by=1),1]$Department 
                                            ])+
  theme_lz_ppt()+geom_text(aes(label=prt),position = position_stack(),hjust=1, color="white", size = 9)+
  coord_flip()+theme(axis.text.x = element_blank())+
  theme(axis.text.y=element_text(size = 20))+
  labs(x="",y="",title=str_wrap("Faculty Tenure Status for Medium-size Departments (5-20 faculty)",35))
```

```{r n<5}
#14 medium departments
data%>%filter(Department %in% ndep[ndep$cnt<5,1]$Department ) %>%
  group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  ggplot(aes(x=Department,y=prt,fill=`Tenure Status`))+geom_bar(stat = "identity")+
  scale_x_discrete(limits = dep.order[dep.order %in% 
                                              ndep[ndep$cnt<5,1]$Department 
                                            ])+
  theme_lz_ppt()+geom_text(aes(label=prt),position = position_stack(),hjust=1, color="white", size = 9)+
  coord_flip()+theme(axis.text.x = element_blank())+
  theme(axis.text.y=element_text(size = 20))+
  labs(x="",y="",title=str_wrap("Faculty Tenure Status for Medium-size Departments (<5 faculty)",35))
```