---
title: "FacultyTenure"
author: "Linli Zhou"
date: "2022-09-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
library(readxl)
library(tidyverse)
```

```{r load data}
data<-read_excel("/Users/linlizhou/Documents/LASELL/Faculty Data for Analyst Candidates.xlsx")
```

```{r}
theme_lz <- function(){ 
    font <- "Helvetica"   #assign font family up front
    theme_minimal() %+replace%    #replace elements already strips axis lines, 
    theme(
      panel.grid.major = element_blank(),    #strip major gridlines
      panel.grid.minor = element_blank(),    #strip minor gridlines
      plot.title = element_text(family = font, size = 9, face = 'bold',hjust = 0.5, vjust = 2),
      axis.title = element_text(family = font, size = 9), 
      axis.text = element_text(family = font, size = 9), 
      axis.text.x = element_text(family = font, size = 9, margin = margin(t=5,b=10)),
      axis.ticks = element_blank(),          #strip axis ticks
      axis.text.y=element_blank(),
      legend.title = element_text(family = font, size=9),
      legend.text = element_text(family = font, size=7),
      legend.position="right",
      
      strip.text = element_text(family = font, size = 9, margin = margin(t=5,b=10)),#move up is + 1
      strip.background = element_blank()
    )}
mycolors<-c("#13294b","#5c88da","#69b3e7","#da291c","#641F45","#fcb53b","#6C6F70")#1-3blue,4-5red,6yellow,7grey
```


# Research questions

- Who/what job titles are those tenured/non tenured 
- Prt of each job title that tenured = tenured in job1/ all people in job1

- T/NT prt (out of all T/NT total in each year) by year
- T/NT prt (out of all T/NT total in each department) by department


- Gender equity: female tenured/ all female vs male
- Gender equity by department: in department 1, calcualte male-female prt gap, then rank

- Racial equity: tenured in race1/ all people in race1
- Gender equity by department: in department 1, calcualte white-black prt gap, then rank

```{r clean}
#remove duplicated rows
data<-unique(data)#from 4003 to 3984 observations
#remove duplicated ID/persons
unique(data$ID)%>%length()#1147 unique ID
data%>% group_by(ID) %>% summarise(cnt=n()) %>%arrange(-cnt) %>%filter(cnt>1) #815 duplicated IDs

```

Tenured percentage has been increased since 2016 from 40% to 44% in 2021, with 2020 being the highest 45%. Non-tenured faculty percentage has been decreased from 60% to 56%, with 2020 being the lowest 55%. There are still 12% less tenured faculty than non tenured. 

```{r unique TvsN across year}
data%>%group_by(Year, `Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits=0))%>%
  ggplot(aes(color=factor(`Tenure Status`),x=factor(Year),y=prt,group=factor(`Tenure Status`)))+geom_line()+
  geom_text(aes(label=prt),fontface="bold")+
  theme_lz()+
  scale_y_continuous(breaks = seq(.4,.6,by=.05),labels = scales::percent)+
  labs(title="Tenured Status by Year",x="Year",y="")+
   scale_color_manual(values = c(mycolors[5],mycolors[2]),labels=c("Non-tenure","Tenure"),name="")+
  theme(axis.text.y=element_blank())
#scale_color_manual(values = c("Non-tenure"=mycolors[4],"Tenure"=mycolors[1]),name="")
#geom_bar(stat = "identity", position=position_dodge())
```

```{r TvsN across year, include=FALSE}
data%>%group_by(Year, `Tenure Status`)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits=0))%>%
  ggplot(aes(color=factor(`Tenure Status`),x=factor(Year),y=prt,group=factor(`Tenure Status`)))+geom_line()+
  geom_text(aes(label=prt))+
  
  theme_lz()+
  scale_y_continuous(breaks = seq(.4,.6,by=.05),labels = scales::percent)+
  labs(title="",x="Year",y="")+
   scale_color_manual(values = c(mycolors[4],mycolors[2]),labels=c("Non-tenure","Tenure"),name="")
#scale_color_manual(values = c("Non-tenure"=mycolors[4],"Tenure"=mycolors[1]),name="")
#geom_bar(stat = "identity", position=position_dodge())
```

```{r}
data%>% filter(Rank=="Professor"|Rank=="Assistant Professor"| Rank=="Associate Professor")%>%
  group_by(Rank,`Tenure Status`)%>%summarise(cnt=n_distinct(ID))%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits=0))%>%
ggplot(aes(fill=factor(`Tenure Status`),x=factor(Rank),y=prt))+
  geom_bar(stat = "identity",position = position_dodge())+
  geom_text(aes(label=prt),position=position_dodge(.9),vjust=1.5,color="white",fontface="bold")+theme_lz()+
  scale_fill_manual(values=c(mycolors[5],mycolors[2]),labels=c("Non-tenure","Tenure"),name="")+
  labs(x="",y="",title="Tenured Status by Rank")
```




